### 2020-05-05 CV/cv-sections/papers.tex
cv update, site update
cv update
added new papers

@@

\cventry
{Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Yura Malitsky} % Role
{Revisiting Stochastic Extragradient} % Title
{} % Location
{May 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://sgo-workshop.github.io}{NeurIPS 2019 Workshop: Bridging Game Theory and Deep Learning}}
		\item {\href{https://arxiv.org/abs/1905.11373}{arXiv 2019}}
	\end{cvitems}
}

@@

\cventry
{Dmitry Kovalev, Samuel Horváth, Peter Richtárik} % Role
{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
{} % Location
{Jan. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1901.08689}{arXiv 2019}}
	\end{cvitems}
}

>>>>

\cventry
{Grigory Malinovsky, Dmitry Kovalev, Elnur Gasanov, Laurent Condat, Peter Richtárik} % Role
{From Local SGD to Local Fixed Point Methods for Federated Learning} % Title
{} % Location
{Apr. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/pdf/2004.01442.pdf}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Zhize Li, Dmitry Kovalev, Xun Qian, Peter Richtárik} % Role
{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} % Title
{} % Location
{Feb. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/pdf/2002.11364.pdf}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Dmitry Kovalev, Robert M. Gower, Peter Richtárik, Alexander Rogozin} % Role
{Fast Linear Convergence of Randomized BFGS} % Title
{} % Location
{Feb. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/pdf/2002.11337.pdf}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Filip Hanzely, Dmitry Kovalev, Peter Richtárik} % Role
{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} % Title
{} % Location
{Feb. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/pdf/2002.04670.pdf}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Sélim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtárik, Adil Salim, Martin Takáč} % Role
{Distributed Fixed Point Methods with Compressed Iterates} % Title
{} % Location
{Dec. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/pdf/1912.09925.pdf}{arXiv 2019}}		
	\end{cvitems}
}

@@

\cventry
{Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Yura Malitsky} % Role
{Revisiting Stochastic Extragradient} % Title
{} % Location
{May 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://sgo-workshop.github.io}{NeurIPS 2019 Workshop: Bridging Game Theory and Deep Learning}}
		\item {\href{https://arxiv.org/abs/1905.11373}{arXiv 2019}}
		\item Accepted to AISTATS 2020
	\end{cvitems}
}

@@

\cventry
{Dmitry Kovalev, Samuel Horváth, Peter Richtárik} % Role
{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
{} % Location
{Jan. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1901.08689}{arXiv 2019}}
		\item Ассepted to ALT 2020
	\end{cvitems}
}
